Hypotheses

### 2019-09-27 analysis/output/figures/Marginal Posterior Visualizations/Hypotheses.Rmd
Updating R Markdown to include plots of all attribute levels.

---
title: "Hypotheses"
output: github_document
---

The purpose of this R Markdown is to visualize the results to the hypotheses proposed at the beginning of the paper.

@@

#### In this study, we simultaneously account for the interaction between legal crackdown, issue area, funding source, and managerial practices as well as donor characteristics. We hypothesize that each of these structural and organizational characteristics will have a significant effect on donor behavior, but we’re unsure of the direction of that effect.

```{r overall, echo = FALSE, warning = FALSE}
# Plot marginals
if (intercept == 1) {
  draws %>% 
    mutate(
      levels = factor(i, labels = level_labels)
    ) %>%
   # filter(levels == str_c("Issue area: ", c("Environment", "Human rights", "Refugee relief"))) %>% 
    ggplot(aes(x = Theta, y = levels)) + 
    geom_density_ridges(scale = 5, height = 3, rel_min_height = 0.01) +
    geom_vline(xintercept = 0, color = "white") +
    labs(y = "Attribute Levels")
}
if (intercept != 1) {
  draws %>% 
    filter(j != 1) %>% 
    mutate(
      levels = factor(i, labels = level_labels), 
      covariates = factor(j, labels = covariate_labels)  
    ) %>%
    ggplot(aes(x = Theta, y = covariates)) +
       geom_density_ridges(scale = 5, height = 3, rel_min_height = 0.01) +
       geom_vline(xintercept = 0, color = "white") +
       labs(y = "Covariates") +
       facet_wrap(~ levels, ncol = 5)
}
```

#### Do donors care if nonprofits they care about are criticized by or kicked out of the countries they work in?

@@

#### Do managerial practices (financial transparency and accountability systems), funding sources (private donations and government grants), and issue areas (emergency response, environmental issues, human rights, and refugee relief) also serve as heuristics that signal an organization’s deservingness to donors?

@@

```{r managerial-practices, echo = FALSE}
# Plot marginals
if (intercept == 1) {
  draws %>% 
    mutate(
      levels = factor(i, labels = level_labels)
    ) %>%
    filter(levels == c( "Financial transparency: Yes",
  "Accountability: Yes")) %>% 
    ggplot(aes(x = Theta, y = levels)) + 
    geom_density_ridges(scale = 5, height = 3, rel_min_height = 0.01) +
    geom_vline(xintercept = 0, color = "white") +
    labs(y = "Attribute Levels")
}
if (intercept != 1) {
  draws %>% 
    filter(j != 1) %>% 
    mutate(
      levels = factor(i, labels = level_labels), 
      covariates = factor(j, labels = covariate_labels)  
    ) %>%
    ggplot(aes(x = Theta, y = covariates)) +
       geom_density_ridges(scale = 5, height = 3, rel_min_height = 0.01) +
       geom_vline(xintercept = 0, color = "white") +
       labs(y = "Covariates") +
       facet_wrap(~ levels, ncol = 5)
}
```

#### 2. Funding Sources
```{r funding_sources, echo = FALSE}
# Plot marginals
if (intercept == 1) {
  draws %>% 
    mutate(
      levels = factor(i, labels = level_labels)
    ) %>%
    filter(levels ==   str_c("Funding sources: ", c("Handful of wealthy private donors", "Government grants"))) %>% 
    ggplot(aes(x = Theta, y = levels)) + 
    geom_density_ridges(scale = 5, height = 3, rel_min_height = 0.01) +
    geom_vline(xintercept = 0, color = "white") +
    labs(y = "Attribute Levels")
}
if (intercept != 1) {
  draws %>% 
    filter(j != 1) %>% 
    mutate(
      levels = factor(i, labels = level_labels), 
      covariates = factor(j, labels = covariate_labels)  
    ) %>%
    ggplot(aes(x = Theta, y = covariates)) +
       geom_density_ridges(scale = 5, height = 3, rel_min_height = 0.01) +
       geom_vline(xintercept = 0, color = "white") +
       labs(y = "Covariates") +
       facet_wrap(~ levels, ncol = 5)
}
```

@@

```{r issue-areas, echo = FALSE, warning = FALSE}
# Plot marginals
if (intercept == 1) {
  draws %>% 
    mutate(
      levels = factor(i, labels = level_labels)
    ) %>%
    filter(levels == str_c("Issue area: ", c("Environment", "Human rights", "Refugee relief"))) %>% 
    ggplot(aes(x = Theta, y = levels, fill = levels)) + 
    geom_density_ridges(scale = 5, height = 3, rel_min_height = 0.01) +
    geom_vline(xintercept = 0, color = "white") +
    labs(y = "Attribute Levels")
}
if (intercept != 1) {
  draws %>% 
    filter(j != 1) %>% 
    mutate(
      levels = factor(i, labels = level_labels), 
      covariates = factor(j, labels = covariate_labels)  
    ) %>%
    ggplot(aes(x = Theta, y = covariates)) +
       geom_density_ridges(scale = 5, height = 3, rel_min_height = 0.01) +
       geom_vline(xintercept = 0, color = "white") +
       labs(y = "Covariates") +
       facet_wrap(~ levels, ncol = 5)
}

>>>>

---
title: "Hypotheses"
date: "Last run: `r format(Sys.time(), '%B %e, %Y')`"
output: github_document
---
In this study, we simultaneously account for the interaction between legal crackdown, issue area, funding source, and managerial practices as well as donor characteristics. We hypothesize that each of these structural and organizational characteristics will have a significant effect on donor behavior, but we’re unsure of the direction of that effect.

@@

### Combined Results

```{r combined-results, echo = FALSE, warning = FALSE}

if (intercept == 1) {
  draws %>% 
    mutate(
      levels = factor(i, labels = level_labels)
    ) %>%
   # filter(levels == str_c("Issue area: ", c("Environment", "Human rights", "Refugee relief"))) %>% 
    ggplot(aes(x = Theta, y = levels)) + 
    # error.bars() +
    geom_density_ridges(scale = 5, height = 3, rel_min_height = 0.01) +
    geom_vline(xintercept = 0, color = "white") +
    labs(y = "Attribute Levels")
}
if (intercept != 1) {
  draws %>% 
    filter(j != 1) %>% 
    mutate(
      levels = factor(i, labels = level_labels), 
      covariates = factor(j, labels = covariate_labels)  
    ) %>%
    ggplot(aes(x = Theta, y = covariates)) +
       geom_density_ridges(scale = 5, height = 3, rel_min_height = 0.01) +
       geom_vline(xintercept = 0, color = "white") +
       labs(y = "Covariates") +
       facet_wrap(~ levels, ncol = 5)
}
```

### Relationship With Host Government

@@

### Organizational Characteristics

@@

```{r managerial-practices, echo = FALSE}
# Plot marginals
if (intercept == 1) {
  draws %>% 
    mutate(
      levels = factor(i, labels = level_labels)
    ) %>%
    filter(levels == c( "Financial transparency: Yes",
  "Accountability: Yes")) %>% 
    ggplot(aes(x = Theta, y = levels)) + 
    geom_density_ridges(scale = 5, height = 3, rel_min_height = 0.01) +
    geom_vline(xintercept = 0, color = "grey") +
    labs(y = "Attribute Levels")
}
if (intercept != 1) {
  draws %>% 
    filter(j != 1) %>% 
    mutate(
      levels = factor(i, labels = level_labels), 
      covariates = factor(j, labels = covariate_labels)  
    ) %>%
    ggplot(aes(x = Theta, y = covariates)) +
       geom_density_ridges(scale = 5, height = 3, rel_min_height = 0.01) +
       geom_vline(xintercept = 0, color = "white") +
       labs(y = "Covariates") +
       facet_wrap(~ levels, ncol = 5)
}
```

#### 2. Funding Sources
```{r funding_sources, echo = FALSE}
# Plot marginals
if (intercept == 1) {
  draws %>% 
    mutate(
      levels = factor(i, labels = level_labels)
    ) %>%
    filter(levels ==   str_c("Funding sources: ", c("Handful of wealthy private donors", "Government grants"))) %>% 
    ggplot(aes(x = Theta, y = levels)) + 
    geom_density_ridges(scale = 5, height = 3, rel_min_height = 0.01) +
    geom_vline(xintercept = 0, color = "grey") +
    labs(y = "Attribute Levels")
}
if (intercept != 1) {
  draws %>% 
    filter(j != 1) %>% 
    mutate(
      levels = factor(i, labels = level_labels), 
      covariates = factor(j, labels = covariate_labels)  
    ) %>%
    ggplot(aes(x = Theta, y = covariates)) +
       geom_density_ridges(scale = 5, height = 3, rel_min_height = 0.01) +
       geom_vline(xintercept = 0, color = "white") +
       labs(y = "Covariates") +
       facet_wrap(~ levels, ncol = 5)
}
```

@@

```{r issue-areas, echo = FALSE, warning = FALSE}
# Plot marginals
if (intercept == 1) {
  draws %>% 
    mutate(
      levels = factor(i, labels = level_labels)
    ) %>%
    filter(levels == str_c("Issue area: ", c("Environment", "Human rights", "Refugee relief"))) %>% 
    ggplot(aes(x = Theta, y = levels)) + 
    geom_density_ridges(scale = 5, height = 3, rel_min_height = 0.01) +
    geom_vline(xintercept = 0, color = "grey") +
    labs(y = "Attribute Levels")
}
if (intercept != 1) {
  draws %>% 
    filter(j != 1) %>% 
    mutate(
      levels = factor(i, labels = level_labels), 
      covariates = factor(j, labels = covariate_labels)  
    ) %>%
    ggplot(aes(x = Theta, y = covariates)) +
       geom_density_ridges(scale = 5, height = 3, rel_min_height = 0.01) +
       geom_vline(xintercept = 0, color = "white") +
       labs(y = "Covariates") +
       facet_wrap(~ levels, ncol = 5)
}

```
### Organization
```{r organization, echo = FALSE, warning = FALSE}
# Plot marginals
if (intercept == 1) {
  draws %>% 
    mutate(
      levels = factor(i, labels = level_labels)
    ) %>%
    filter(levels == str_c("Organization: ", c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross"))) %>% 
    ggplot(aes(x = Theta, y = levels)) + 
    geom_density_ridges(scale = 5, height = 3, rel_min_height = 0.01) +
    geom_vline(xintercept = 0, color = "grey") +
    labs(y = "Attribute Levels")
}
if (intercept != 1) {
  draws %>% 
    filter(j != 1) %>% 
    mutate(
      levels = factor(i, labels = level_labels), 
      covariates = factor(j, labels = covariate_labels)  
    ) %>%
    ggplot(aes(x = Theta, y = covariates)) +
       geom_density_ridges(scale = 5, height = 3, rel_min_height = 0.01) +
       geom_vline(xintercept = 0, color = "white") +
       labs(y = "Covariates") +
       facet_wrap(~ levels, ncol = 5)
}
